\section*{Achievements} Achievements
After researching and implementing the project, I have completed the development and evaluation of a mobile application solution for small businesses to assist in managing sales and inventory. The application was developed using the Flutter framework and utilized Firebase as the data platform. The specific objectives of the research were to:
\begin{itemize}
    \item Investigate challenges faced by small businesses in managing sales and inventory.
    \item Develop a mobile application solution for small businesses using the Flutter framework and Firebase.
    \item Evaluate the usability and effectiveness of the developed application through user testing and surveys.
\end{itemize}

The outcomes of this study will contribute to the knowledge of mobile application solutions for small businesses.

\section*{Limitations}
\begin{itemize}
    \item The interface is still simple
    \item Self-researched data is not entirely correct
    \item Not all functions have been processed for each form.
    \item Only search by ID is correct because Firebase does not support full-text search
    \item Although the data has image URLs, images cannot be loaded from Google Cloud.
\end{itemize}

\section*{Development Direction} 
Due to limited knowledge, it is necessary to learn and use retail business processing more effectively. In addition, some other functional modules need to be added for better software operation such as adding invoice and type constraints, adding data flow processing as well as better error handling from Firebase.